Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-28 colt-21/cvx-flats.tex
Adding flow DAG of results

\usepackage{mathtools, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage{caption}
% NOTE: had to comment out "todo" in colt2021.cls
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

@@

\begin{table}
	\begin{center}
	\begin{tabular}{|p{12ex}||l|l|} 
		\hline
		& \emph{Target loss}  & \emph{Target statistic}\\ \hline \hline
		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical prediction\\ 
		{\em prediction} & & \\ \hline 
		\emph{Continuous } & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
		\emph{estimation}& & \\
		\hline
	\end{tabular}
\caption{The four quadrants of problem types, with an example of interest for each.}
\label{tab:quadrants}
\end{center}
\end{table}

>>>>

\usepackage{mathtools, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage{caption}
% NOTE: had to comment out "todo" in colt2021.cls
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}
\usetikzlibrary{arrows}

@@

\begin{table}
	\begin{center}
	\begin{tabular}{|p{12ex}||l|l|} 
		\hline
		& \emph{Target loss}  & \emph{Target statistic}\\ \hline \hline
		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical prediction\\ 
		{\em prediction} & & \\ \hline 
		\emph{Continuous } & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
		\emph{estimation}& & \\
		\hline
	\end{tabular}
\caption{The four quadrants of problem types, with an example of interest for each.}
\label{tab:quadrants}
\end{center}
\end{table}
\begin{center}
\resizebox{0.7\linewidth}{!}{%
\begin{tikzpicture}

\tikzset{vertex/.style = {shape=circle,draw,minimum size=10em}}
\tikzset{edge/.style = {->,> = triangle 45, thick}}
\tikzset{node/.style = {anchor=above, sloped}}

% vertices
\node[vertex] (consis-ell) at  (-2,4) {Consistency w.r.t. $\ell$};
\node[vertex] (consis-gam) at  (4,4) {Consistency w.r.t. $\gamma$};
\node[vertex] (indir-elic) at  (-2,-4) {Indirect elicitation};
\node[vertex] (d-flats) at  (4,-4) {$d$-flats};
\node[vertex] (conscvx-bd) at (8,0) {$\conscvx(\gamma) > d$};
\node[vertex] (q1-bounds) at (12,4) {$\conscvx$ bounds for Q1};
\node[vertex] (q4-bounds) at (12,-4) {$\conscvx$ bounds for Q4};

%edges
\draw[edge, <->] (consis-ell) to node[above]{Lemma~\ref{lem:consistent-loss-implies-prop}} (consis-gam);
\draw[edge] (consis-gam) to node[above, sloped]{Theorem~\ref{thm:consistent-implies-indir-elic}} (indir-elic);
\draw[edge] (indir-elic) to node[above, sloped]{Lemma~\ref{lem:convex-flats-inf-dim}} (d-flats);
\draw[edge] (d-flats) to node[above, sloped]{{\footnotesize Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}}} (conscvx-bd);
\draw[edge] (consis-gam) to node[above, sloped]{\footnotesize {Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}}} (conscvx-bd);
\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:finite-calib}} (q1-bounds);
\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:contin-consis}} (q4-bounds);

\end{tikzpicture}
}
\end{center}
